\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-19 icse/eval.tex
Evaluation except last quetion

\begin{table}
  \centering
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794} \\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\ \hdashline
    In-process features & \inred{XXXX} \\\hdashline
    Module tests & \inred{XXXX} \\\hdashline
    Non-strict tests & \inred{XXXX} \\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Strict Script Tests} & \textbf{\inred{XXXXX}} \\
    \aboverulesepcolor{gainsboro}\midrule
    Not supported features & \inred{XXXX} \\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}} \\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XXXX} \\\hdashline
    Failed tests & \inred{XXXX} \\\bottomrule
  \end{tabular}
  \caption{The results of tests in the test262 for ECMAScript 2020.}
  \label{table:test262}
\end{table}

To evaluate that \( \tool \) correctly extracts semantics, we extract semantics of ECMAScript
2020 via our tool. Above automatically extracted parts of semantics, we manually implement
\inred{XX} \( \ires \) functions for failed to be automatically compiled abstract algorithms.
Moreover, we fill in global setting based on ECMAScript 2020 specification as described
in Section~\ref{sec:framework}. The ECMAScript 2020 version is actively updated in
GitHub~\ref{es2020} to be released in the next year. Ecma Technical Committee 39 (TC39)
officially provides the conformance test suite, test262, for ECMAScript 2020.
Thus, we decide to evaluate the correctness of our syntax and semantics based on the test262.
However, the test262 also provides tests for in-process features and other extensions
such as web browsers and internationalisation. Thus, we exclude them from our target tests.
Figure~\ref{table:test262} describes how to break down tests and the test results of extracted
semantics. We use test262 written in \inred{August 6, 2019}. In that version,
test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
for extensions and in-process features. Then, we remove tests for non-strict mode because
we focus on only JavaScript codes in strict mode
as described in Section~\ref{sec:framework}. Finally, we remove the \inred{XXXX} tests
for not supported language features such as \inred{modules, JSON, RegExp, or Date}.
We test our extracted semantics for \inred{XXXXX} applicable tests and pass \inred{XXXX} tests.
There are several reasons of test failures; \inred{...}.

@@

\begin{table}
  \centering
  \[
    \begin{array}{l|r|r|r|r} \hline
      \text{features} &
      \multicolumn{1}{c|}{\text{\#prods}} &
      \multicolumn{1}{c|}{\text{\#steps}} &
      \multicolumn{1}{c|}{\Delta\text{CR}} &
      \multicolumn{1}{c}{\text{tests}}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \text{\inred{????}} & \inred{X} & \inred{XX} & \inred{X} & \inred{XX/XX}\\\hline
      \hline
      \text{total} & \inred{XX} & \inred{XXX} & \inred{XX} & \inred{XXX/XXX}\\\hline
    \end{array}
  \]
  \caption{The result of \( \tool \) for in-process language features}
  \label{table:in-process}
\end{table}

We also check that \( \tool \) deals with future language features for adaptability.
ECMAScript specifications are managed as open-sources and proposals of in-process language
features follow the TC39 process and are tracked in the separated repository~\ref{proposals}.
Thare are five stages for proposals; Stage 0, Stage 1, active, finished or inactive proposals.
Each proposal starts from Stage 0 and is promoted to an active proposal through Stage 1.
Then, the committee (TC39) regularly examins the active proposal and changes the stage into
finished if they want to apply the proposed language features, otherwise, changes it
into inactive stage.

% We also check that \( \tool \) deals with future language features based on in-process language
% features. Each in-process language feature has its own specification, and the test262 supports
% tests for them. We extract semantics of \inred{XX} language features via \( \tool \) and test extracted
% semantics based on tests in test262. Table~\ref{table:in-process} describes the result and
% \( \tool \) successfully generates parsers of total \inred{XX} productions.
% For semantics, \( \tool \) successfully compiles \inred{XXX} algorithm steps by adding
% \inred{XX} more compile rules. Above the semantics, \inred{XXX} tests passes among \inred{XXX}
% tests for \inred{XX} in-process language features.

@@

We found four specification errors in ECMAScript 2020. All of them

>>>>

\begin{table}
  \centering
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794} \\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\ \hdashline
    In-progress features & \inred{XXXX} \\\hdashline
    Module tests & \inred{XXXX} \\\hdashline
    Non-strict tests & \inred{XXXX} \\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Strict Script Tests} & \textbf{\inred{XXXXX}} \\
    \aboverulesepcolor{gainsboro}\midrule
    Not supported features & \inred{XXXX} \\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}} \\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XXXX} \\\hdashline
    Failed tests & \inred{XXXX} \\\bottomrule
  \end{tabular}
  \caption{The results of tests in the test262 for ECMAScript 2020.}
  \label{table:test262}
\end{table}

To evaluate that \( \tool \) correctly extracts semantics, we extract semantics of ECMAScript
2020 via our tool. Above automatically extracted parts of semantics, we manually implement
\inred{XX} \( \ires \) functions for abstract algorithms failed to be automatically compiled.
Moreover, we fill in global setting based on ECMAScript 2020 specification as described
in Section~\ref{sec:framework}. The ECMAScript 2020 version is actively updated in
GitHub~\cite{es2020} to be released in the next year. Ecma Technical Committee 39 (TC39)
officially provides the conformance test suite, test262, for ECMAScript 2020.
Thus, we decide to evaluate the correctness of our syntax and semantics based on the test262.
However, the test262 also provides tests for in-progress features and other extensions
such as web browsers and internationalisation. Thus, we exclude them from our target tests.
Figure~\ref{table:test262} describes how to break down tests and the test results of extracted
semantics. We use test262 written in \inred{August 6, 2019}. In that version,
test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
for extensions and in-progres features. Then, we remove tests for non-strict mode because
we focus on only JavaScript codes in strict mode
as described in Section~\ref{sec:framework}. Finally, we remove the \inred{XXXX} tests
for not supported language features such as \inred{modules, JSON, RegExp, or Date}.
We test our extracted semantics for \inred{XXXXX} applicable tests and pass \inred{XXXX} tests.
There are several reasons of test failures; \inred{...}.

@@

We also check that \( \tool \) deals with future language features for adaptability.
ECMAScript specifications are managed as open-sources and proposals of in-progress language
features follow the TC39 process and are tracked in the separated repository~\cite{proposals}.
Thare are five stages for proposals; Stage from 0 to 3, and finished or inactive proposals.
The committee (TC39) regularly examins the proposals in Stage 3 and changes the stage into
finished if its members decide to apply it into official specifications. Otherwise, the committee
changes the stage of proposal into inactive. Our tool \( \tool \) is also applicable into
not yet finished proposals and we advance \inred{a case study for a proposal} in Stage 3.
We decide to study on proposals in Stage 3 because test262 supports tests for several
proposals in Stage 3.

\inred{...}

@@

We found four specification errors in ECMAScript 2020 via \( \tool \).
They were all confirmed by TC39 and will be fixed in the next release.

\paragraph{Ambiguous \textbf{VarScopedDeclarations} for \textit{IterationStatement}}
